Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-09-20 ICLR25/Paper_noProof.tex
section 4
experiments.

\newcommand{\toolname}{\CMP}

@@

In this paper, we study the MILP encoding of ReLU-DNNs, and provide new deep insights in the LP relaxation. This allows us to carefully craft a {\em partial MILP} solution which selects automatically few neurons encoded as integer variables, the rest using the LP relaxation. Compared with previous attempts, we can reduce the number of integer variables by around 4 times while maintaining the same level of accuracy. This gives rise to a very efficient yet accurate algorithm. Implemented in {\em Hybrid MILP (hMILP)}, calling first $\alpha,\beta$-CROWN with a short time-out to solve easier instances, and then partial MILP for those for which $\alpha,\beta$-CROWN fails, produces a very accurate yet efficient verifier, reducing tremendously the gap of undecided instances ($8-15\%$), while keeping a reasonable runtime ($<500s$ on average per instance).
\end{abstract}

@@

\input{comppaths}

\begin{table}
	\centering
	\begin{tabular}{||l||c|c|c|c||c||}
		\hline \hline
		 & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & Refined & Hybrid \\ 
		 Network & TO=10s & TO=30s & TO=2000s & $\beta$-Crown & MILP \\ 
		\hline
		MNIST 6$\times$100 & 57\% (6.9s) & 55\% (18.9s) & 50\% (1026s) & 13\% 
		(92s) & 13\% \bf (46s) \\ \hline
		MNIST 6$\times$200 & 50\% (6.5s) & 47\% (17s) & 46\% (930s) & 9\% (80s) & \bf 8\% (71s) \\ \hline
		MNIST 9$\times$100 & 63\% (7.2s) & 58\% (20s) & 58\% (1163s) & 21\% (102s) & \bf 15\% (61s) \\ \hline
		MNIST 9$\times$200 & 56\% (6.8s) & 55\% (18s) & 54\% (1083s) & 16\% (83s) & \bf 8\% (78s) \\ \hline
		MNIST 6$\times$500 & 53\% (6.4s) & 51\% (16s) & 50\% (1002s) & N/A & 
		\bf 10\% (402s) \\ \hline
		CIFAR CNN-B-adv & 28\% (4.3s) & 22\% (8.7s) & 20\% (373s) & N/A & \bf 11\% (417s) \\ \hline \hline
		CIFAR Resnet & 0\% (2s) & 0\% (2s) & 0\% (2s) & N/A & 0\% (2s) \\ \hline \hline
	\end{tabular}
	\caption{Gap $\%$ between attackable images and verifiable images ({\em lower is better}), as certified by $\alpha,\beta$-Crown, refined $\beta$-Crown and Hybrid MILP, run on 7 DNNs (average runtime per image in second). The 6 first DNNs are hard instances, while the last one (ResNet) is an easy instance (it is trained to be easy to verify using Wong, but with a very low accuracy level), provided for reference.}
	\label{table_hybrid}
	\end{table}

>>>>

\newcommand{\toolname}{Hybrid MILP}

@@

In this paper, we study the MILP encoding of ReLU-DNNs, and provide new deep insights in the LP relaxation. This allows us to carefully craft a {\em partial MILP} solution which selects automatically few neurons encoded as integer variables, the rest using the LP relaxation. Compared with previous attempts, we can reduce the number of integer variables by around 4 times while maintaining the same level of accuracy. Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-CROWN with a short time-out to solve easier instances, and then partial MILP for those for which $\alpha,\beta$-CROWN fails, produces a very accurate yet efficient verifier, reducing tremendously the gap of undecided instances ($8\%$-$15\%$), while keeping a reasonable runtime ($46s$-$417s$ on average per instance).
\end{abstract}

@@

\input{formula}

### 2024-09-20 ICLR25/experiments.tex
experiments.

%
We implemented \toolname in Python 3.8, and Gurobi 9.52 was used for solving LP and MILP problems. We conducted our evaluation on an AMD 5975WX  ($32$ cores$@3.6$GHz, 7nm, year 2022) 
with 256 GB of main memory and an NVIDIA RTX 3090 (not used for CMP).

We conducted our evaluation on neural networks obtained from the ERAN GitHub (\url{https://github.com/eth-sri/eran}, the 4th to the 8th DNNs provided).
These verification-agnostic DNNs have varying sizes: $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$ and $6 \times 500$. We selected the 4 first because they have been tested in both \cite{prima} and \cite{crown}, they have good accuracy ($>94\%$ \cite{prima}), 
and depite their small sizes there is still a large portion ($12\%$ to $20\%$) of images which are {\em undetermined} by these SOTA methods, that is images neither verified nor for which an attack has been found  \cite{attack}. Hence more accurate methods are useful. 
The next DNN in the list was the larger $6 \times 500$ DNN, which seemed an interesting challenge (very high accuracy and few attacks) to understand the scaling of CMP. Interestingly, tests on $6 \times 500$ were not reported in \cite{prima} nor in \cite{crown}. All these DNNs tackle the MNIST benchmark, which is not a limitation as we want to validate that focusing on compensating strength improves the accuracy: we do not claim that the particular CMP implementation is the most efficient in all the situations.

@@

\begin{enumerate}
	\item How does the the choice of the set $Z$ impacts the accuracy of $\MILP_Z$? 
	\item Can compensating strength, as implemented in CMP, outperform accuracy of the SOTA? 
\end{enumerate}

\subsection{Utility of Heuristic based on Compensation Strength  }

%The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes,  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
To measure the impact of the heuristic based on compensation strength, we focused on the smallest DNN (i.e. $5\times 100$) so as to obtain exact bounds for the first few layers using a full MILP encoding of the DNN. We tested over the $\vx=59$th image in the MNIST dataset, as it has a large number of unstable ReLU nodes in the first few layers ($61$ in the first and $55$ in the second layer), so we can experiment with a larger choice of values) for $K$.

To measure the accuracy, we measure the uncertainty of all nodes in a layer:
the uncertainty of a node is the range between its computed lower and upper bound. 
We then average the uncertainty among all the nodes of the layer.
Formally, the uncertainty of a node $n$ with bounds $[\alpha,\beta]$ is $unc(a) = \beta - \alpha$. The average uncertainty of layer $\ell$ is $\dfrac{\sum_{a\in l} unc(a)}{size(\ell)}.$

@@

\begin{table}[t!]	
	\centering
	\begin{tabular}{|c||c|c|c|}
		\hline
		\text{Number $K$}  &  \bf Utility&  \text{Incoming Weights} \cite{ DivideAndSlide} & \text{Random} \\ \hline
		\hline
		0  &   1.761  & 1.761 & 1.761  \\ \hline
		5  & \bf 1.532  & &   \\ \hline
		10  & \bf 1.371  & 1.651 & 1.696  \\ \hline
		15  & \bf 1.247  &   &   \\ \hline
		20  & \bf 1.145  & 1.557 & 1.619  \\ \hline
		25  & \bf 1.061  &  &   \\ \hline
		30  & \bf 0.989  & 1.489 & 1.546  \\ \hline
		35  & \bf 0.934  &  &   \\ \hline
		40  & \bf 0.914 & 1.447 & 1.469  \\ \hline
		116 (max) &  0.895 & 1.424 (max=$61$) & 0.895  \\ \hline
	\end{tabular}
	\caption{Average uncertainty of $\MILP_Z$ for nodes of the third layer, for $Z$ with $K$ ReLU nodes of the 1st and 2nd layer (utility function vs \cite{ DivideAndSlide} vs random choice).}
	\label{tab:example1}
	\vspace{-0.6cm}
\end{table}

We focus on the uncertainty of nodes in the third layers, wrt ReLU nodes in the first and second layer. The bounds for nodes of the first two layers are computed exactly using the full MILP encoding. Let $d$ be a neuron of the third layer.
We let $\delta_{\pi,\pi'}=1$ if $(\pi,\pi')$ is compensating, 0 otherwise.
We evaluate the pair $(c,c')$ of nodes in the previous (second) layer in the following way: let $comp(c,c')=\sum_{b} \delta(bcd,bc'd) \val_{\vx}(b) \min( weight(bcd),weight(bc'd))$, meaning that we take into account all the sources $b$ such that $(bcd,bc'd)$ is compensating.

We select the pair $(c,c')$ with the highest $comp(c,c')$, and let $Z=\{c,c'\}$.
Then, we add nodes iteratively to $Z$, starting with the highest $comp(c)=\sum_{c' \in Z} comp(c,c')$. Further, we can add nodes $b$ from the first layer, taking into account compensating pairs $(a b c d, a b' c' d)$ for all $\{c,c'\} \in C$. 
Let $comp(b,b')=\sum_a \sum_{c,c' \in Z} \delta(abcd,ab'c'd) \val_{\vx}(a) \min( weight(abcd)$, $weight(ab'c'd))$ and add $b,b'$ to $Z$ with the highest $comp(b,b')$.
We then let $comp(b)=\sum_{b' \in Z} comp(b,b') + comp(b',b)$, and iteratively select nodes $b$ (first layer) or $c$ (second layer) by selecting the heaviest $comp(b)$ or $comp(c)$. The intuition behind the formula is straightforward: $\val_{\vx}(a)weight(abcd)$ is the contribution from node $a$ to the target $d$ using $weight(abcd)$, and min of two paths is a natural value to represent the strength of compensation: if one of them is very small, the effect of compensation will also be very small.

We report in Table \ref{tab:example1} the average uncertainty of $\MILP_Z$ following the choice of the $K$ heaviest compensating ReLU nodes in $Z$, vs choosing $K$ nodes from layers $1$ and $2$. We test using compensation, compared with a random choice, and also choice based on strength in \cite{ DivideAndSlide}, defined as $strength(c) = (UB(n)-LB(n))\cdot W_{cd}$. It is however limited to choosing ReLU in the previous layer 2. This choice is fine for few nodes (10,20), as there is a high correlation between $comp(c)$ being high and $W_{cd}$ being high. However, as soon as many nodes can be chosen in $Z$, compensate becomes much more accurate. Even random becomes more accurate as the number of nodes grows, as \cite{ DivideAndSlide} only has access to nodes $c$ in layer 2, and not to nodes $b$ in layer 1.
For comparison, compensate is the most accurate, from 30 nodes, experimentally validating that compensating strength is the important factor to consider.

@@

\subsection{Comparison with Prior State of the Art}

@@

Finally, we focused on DNNs employing ReLU activation functions since our approached on usage of MILP, which is naturally suited for ReLU activation function. However, it is worth remarking that the notion of compensation strength is independent of activation function, and therefore, an interesting direction of future work would be to explore the impact of compensation strength-based approaches for other activation functions.

>>>>

%
We implemented \toolname\ in Python 3.8, and Gurobi 9.52 was used for solving LP and MILP problems. We conducted our evaluation on an AMD 5975WX  ($32$ cores$@3.6$GHz, 7nm, year 2022) 
with 256 GB of main memory and an NVIDIA RTX 3090.

@@

\begin{enumerate}
	\item How does the the choice of the set $X$ impacts the accuracy of $\MILP_X$? 
	\item How accurate is Hybrid MILP, and how efficient is it?
\end{enumerate}

\subsection{Evaluation of the Utility function to choose nodes to open}

%The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes,  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
To measure the impact of the utility function to select nodes to open, we focused on a small hard DNN, namely $5\times 100$, so as to obtain exact bounds for the first few layers using a full MILP encoding of the DNN. We tested over the $\vx=59$th image in the MNIST dataset, as it has a large number of unstable ReLU nodes in the first few layers ($61$ in the first and $55$ in the second layer), so we can experiment with a larger choice of values) for $K$.
To measure the accuracy, we measure the uncertainty of all nodes in a layer:
the uncertainty of a node is the range between its computed lower and upper bound. 
We then average the uncertainty among all the nodes of the layer.
Formally, the uncertainty of a node $n$ with bounds $[\alpha,\beta]$ is $unc(a) = \beta - \alpha$. The average uncertainty of layer $\ell$ is $\dfrac{\sum_{a\in l} unc(a)}{size(\ell)}.$

@@

\begin{table}[b!]	
	\centering
	\begin{tabular}{|c||c|c|c|}
		\hline
		\text{Number $K$}  &  \bf Utility&  \text{Strength} \cite{ DivideAndSlide} & \text{Random} \\ \hline
		\hline
		0  &   1.761  & 1.761 & 1.761  \\ \hline
		5  & \bf 1.532  & &   \\ \hline
		10  & \bf 1.371  & 1.651 & 1.696  \\ \hline
		15  & \bf 1.247  &   &   \\ \hline
		20  & \bf 1.145  & 1.557 & 1.619  \\ \hline
		25  & \bf 1.061  &  &   \\ \hline
		30  & \bf 0.989  & 1.489 & 1.546  \\ \hline
		35  & \bf 0.934  &  &   \\ \hline
		40  & \bf 0.921 & 1.447 & 1.469  \\ \hline
		116 (max) &  0.895 & 1.424 (max=$61$) & 0.895  \\ \hline
	\end{tabular}
	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the 1st and 2nd layer (our utility function vs \cite{ DivideAndSlide} vs random choice).}
	\label{tab:example1}
	\vspace{-0.6cm}
\end{table}

We focus on the uncertainty of nodes in the third layers, wrt ReLU nodes in the first and second layer. The bounds for nodes of the first two layers are computed exactly using the full MILP encoding. We report in Table \ref{tab:example1} the average uncertainty of $\MILP_X$ following the choice of the $K$ heaviest neurons for our utility function, vs choosing $K$ nodes from layers $1$ and $2$. We compared with a random choice in the first two layers, and also choice based on strength in \cite{DivideAndSlide}, defined as 
$strength(n) = (UB(n)-LB(n))\cdot |W_{cd}|$, which is thus limited to the previous (2sd hidden layer).

The Utility function reveals to select very important nodes: already with 35 out of 116 nodes, the accuracy is improved by $95\%$ what can be done if all 116 nodes are opened compared with LP (K=0). It is also much more accurate than using Incoming weights: already with 5 (resp. 10) nodes chosen by our utility function is more accurate than $20$ (resp. $40$) nodes chosen by Incoming weights. That is more than 4 reduction in the number of nodes necessary for similar accuracy.  Random is even worst Strength up to 30 nodes, then selecting in earlier layers appear to be more useful as there are not so many nodes to open in the previous layer.

@@

\subsection{Comparison with $\alpha,\beta$ Crown}

We conducted our evaluation on the neural networks tested in \cite{crown},
which display a large gap ($\geq 20\%$) between images that can be certified by $\alpha,\beta$-CROWN and the upper bound when we remove those which can be falsified.

Namely, these are 6 {\em hard} ReLU-DNNs: 5 MNIST DNN from the ERAN GitHub (\url{https://github.com/eth-sri/eran}, the 4th to the 8th DNNs provided) as well as 1 CIFAR CNN from 
\cite{AdversarialTrainingAndProvableDefenses}, also see \cite{SDPFI}. 
For reference, we also report an easy but very large ResNet Network for CIFAR10, already tested with $\alpha,\beta$ CROWN. We report in Table \ref{table_hybrid} the $\%$ of undecided images, that is the $\%$ of images than can be neither falsified (by $\alpha,\beta$-CROWN) nor verified by the tested verifier, among the 100 first images for each MNIST or CIFAR10 benchmark.

\begin{table}[t!]
	\centering
	\begin{tabular}{||l||c|c|c|c||c||}
		\hline \hline
		 & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & Refined & Hybrid \\ 
		 Network & TO=10s & TO=30s & TO=2000s & $\beta$-Crown & MILP \\ 
		\hline
		MNIST 5$\times$100 & 57\% (6.9s) & 55\% (18.9s) & 50\% (1026s) & 13\% 
		(92s) & 13\% \bf (46s) \\ \hline
		MNIST 5$\times$200 & 50\% (6.5s) & 47\% (17s) & 46\% (930s) & 9\% (80s) & \bf 8\% (71s) \\ \hline
		MNIST 8$\times$100 & 63\% (7.2s) & 58\% (20s) & 58\% (1163s) & 21\% (102s) & \bf 15\% (61s) \\ \hline
		MNIST 8$\times$200 & 56\% (6.8s) & 55\% (18s) & 54\% (1083s) & 16\% (83s) & \bf 8\% (78s) \\ \hline
		MNIST 6$\times$500 & 53\% (6.4s) & 51\% (16s) & 50\% (1002s) & N/A & 
		\bf 10\% (402s) \\ \hline
		CIFAR CNN-B-adv & 28\% (4.3s) & 22\% (8.7s) & 20\% (373s) & N/A & \bf 11\% (417s) \\ \hline \hline
		CIFAR Resnet & 0\% (2s) & 0\% (2s) & 0\% (2s) & N/A & 0\% (2s) \\ \hline \hline
	\end{tabular}
	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-Crown, refined $\beta$-Crown and Hybrid MILP, run on 7 DNNs (average runtime per image in second). The 6 first DNNs are hard instances, while the last one (ResNet) is an easy instance (it is trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.}
	\label{table_hybrid}
	\end{table}

Interpretation: on easy instances, Hybrid MILP is virtually similar to $\alpha,\beta$-CROWN, 
as it is called first and it is sufficient to have $0\%$ undecided images, as shown even on the very large ResNet.

On hard instances (the 6 first DNNs tested), Hybrid MILP is very accurate, only leaving $8\%$-$15\%$ of images undecided, with runtime taking less than $500s$ in average per image, 10 times less even on smaller DNNs. It can scale up to quite large hard CNN instances, such as CNN-B-Adv with 2M parameters and 20K activations.

Compared with $\alpha,\beta$-Crown with a time-out of TO=2000s, it is much more accurate, with a reduction of undecided images by $9\%$-$43\%$ wrt $\alpha,\beta$-Crown with TO of 2000s. It is also from 20x faster on smaller networks to similar time on the largest DNN.
Compared with $\alpha,\beta$-Crown with a time-out of TO=30s, the accuracy gap is even larger (e.g. $11\%$ for CNN-B-Adv, i.e. half undecided images), although the average runtime is also obviously larger (solving hard istances takes longer than solving easy instances).

Last, compared with refined $\beta$-Crown, we can observe three patterns: on the shallowest DNNs (5x100, 5x200), refined $\beta$-Crown can run full MILP on almost all nodes, reaching almost the same accuracy than our Hybrid MILP, but with longer runtime (up to 2x on 5x100). On intermediate DNNs (8x100,8x200), full MILP invoked by refined $\beta$-Crown can only be run on a fraction of the neurons, and the accuracy is not as good as Hybrid MILP, with $6\%-8\%$ more undecided images, while having longer runtime. Last, refined $\beta$-Crown cannot scale to larger instances (6x500, CNN-B-Adv), while Hybrid MILP can.

These verification-agnostic DNNs have varying sizes: $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$ and $6 \times 500$. We selected the 4 first because they have been tested in both \cite{prima} and \cite{crown}, they have good accuracy ($>94\%$ \cite{prima}), 
and depite their small sizes there is still a large portion ($12\%$ to $20\%$) of images which are {\em undetermined} by these SOTA methods, that is images neither verified nor for which an attack has been found  \cite{attack}. Hence more accurate methods are useful. 
The next DNN in the list was the larger $6 \times 500$ DNN, which seemed an interesting challenge (very high accuracy and few attacks) to understand the scaling of CMP. Interestingly, tests on $6 \times 500$ were not reported in \cite{prima} nor in \cite{crown}. All these DNNs tackle the MNIST benchmark, which is not a limitation as we want to validate that focusing on compensating strength improves the accuracy: we do not claim that the particular CMP implementation is the most efficient in all the situations.

@@

Finally, we focused on DNNs employing ReLU activation functions since our approached on usage of MILP, which is naturally suited for ReLU activation function. However, it is worth remarking that the notion of compensation strength is independent of activation function, and therefore, an interesting direction of future work would be to explore the impact of compensation strength-based approaches for other activation functions. 
\fi

### 2024-09-20 ICLR25/introduction.tex
experiments.

In this paper, we focused on 6 {\em hard} ReLU-DNNs that have been previously tested in one or both of \cite{SDPFI},\cite{crown}, and with a large gap ($>20\%$) between images that can be certified and the upper bound when we remove those which can be falsified. In turns, hard instances does not necessarily mean very large DNNs, the smallest of the DNN considered having only 500 hidden neurons, namely 5x100 for MNIST. We first dwelve into the scaling of $\alpha,\beta$- Crown, to understand how longer Time-Out (TO) affects the number of undecided images and the runtime. Table \ref{table_beta} reveals that even allowing for 200 times longer time outs only improves the verification from 2\% to 8\%, leaving a considerable $20\%-50\%$ gap of undecided images, while necessitating vastly longer runtime (300s-1000s in average per instance).

\begin{table}[t!]
	\centering
	\begin{tabular}{||l|c|c||c|c|c||}
		\hline
		Network & Accuracy & Upper  & $\alpha,\beta$-Crown& $\alpha,\beta$-Crown & $\alpha,\beta$-Crown \\ 
		Perturbation &   & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
		MNIST 6$\times$100 & 99\% & 90\% & 33\% & 35\% & 40\%   \\
		$\epsilon = 0.026$ &  &  & 6.9s &  18.9s &  1026s  \\  \hline
		MNIST 6$\times$200 & 99\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
		$\epsilon = 0.015$ & &  & 6.5s &  16.6s &  930s  \\  \hline
		MNIST 9$\times$100 & 97\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
		$\epsilon = 0.026$ &  &  & 7.2s &  20.1s &  930s  \\  \hline
		MNIST 9$\times$200 & 97\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
		$\epsilon = 0.015$ & &  & 6.8s &  18.2s &  1083s  \\  \hline
		MNIST 6$\times$500 & 100\%  & 94\%  & 41\%  & 43\%  & 44\%   \\ 
		$\epsilon = 0.035$ & &  & 6.4s &  16.4s &  1003s  \\  \hline
		CIFAR CNN-B-adv & 78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
		$\epsilon = 2/255$&  &  & 4.3s & 8.7s & 373s  \\ \hline \hline
		CIFAR ResNet & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
		$\epsilon = 2/255$ &  &  & 2s & 2s & 2s  \\ \hline
	\end{tabular}
	\caption{Images verified by $\alpha,\beta$-Crown with different time-outs (TO) on 7 DNNs, and average runtime per image. The 6 first DNNs are hard instances. The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.}
	\label{table_beta}
	\vspace{-0.3cm}
\end{table}

\begin{table}[b!]
	\centering
	\begin{tabular}{||l|c|c||c|c|c||}
		\hline
		Network &  Accuracy & Upper  & Marabou 2.0 & NNenum? &  Full MILP  \\ \hline
		MNIST 6$\times$100 & 99\% & 90\% & 28\% & $\approx 46\%$ & 40 \%    \\
		$\epsilon = 0.026$ & &  &6200s &  5220s & 6100s
		  \\  \hline
		  MNIST 6$\times$100 & 99\% & 90\% & 28\% & $40\%$ & 37 \%    \\
		  TO=2000s & &  & 1250s  & 1343s & 1466s \\  \hline	
	\end{tabular}
\caption{Complete verifiers run on the smallest of the hard DNN with TO = 10 000s. 
%Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and 
No complete verifier could outperform $\alpha,\beta$-CROWN (40\%, 1026s), despite the much larger runtime.}
\label{table_complete}
\end{table}

>>>>

In this paper, we focused on the 6 {\em hard} ReLU-DNNs that have been previously tested in \cite{crown}, which display a large gap ($>20\%$) between images that can be certified 
by $\alpha,\beta$-CROWN and the upper bound when we remove those which can be falsified. In turns, hard instances does not necessarily mean very large DNNs, the smallest of these hard DNNs having only 500 hidden neurons, namely 5x100 for MNIST. We first dwelve into the scaling of $\alpha,\beta$- Crown, to understand how longer Time-Out (TO) affects the number of undecided images and the runtime. Table \ref{table_beta} reveals that even allowing for 200 times longer time outs only improves the verification from 2\% to 8\%, leaving a considerable $20\%-50\%$ gap of undecided images, while necessitating vastly longer runtime (300s-1000s in average per instance).

\begin{table}[t!]
	\centering
	\begin{tabular}{||l|c|c||c|c|c||}
		\hline
		Network & Accuracy & Upper  & $\alpha,\beta$-Crown& $\alpha,\beta$-Crown & $\alpha,\beta$-Crown \\ 
		Perturbation &   & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
		MNIST 5$\times$100 & 99\% & 90\% & 33\% & 35\% & 40\%   \\
		$\epsilon = 0.026$ &  &  & 6.9s &  18.9s &  1026s  \\  \hline
		MNIST 5$\times$200 & 99\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
		$\epsilon = 0.015$ & &  & 6.5s &  16.6s &  930s  \\  \hline
		MNIST 8$\times$100 & 97\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
		$\epsilon = 0.026$ &  &  & 7.2s &  20.1s &  930s  \\  \hline
		MNIST 8$\times$200 & 97\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
		$\epsilon = 0.015$ & &  & 6.8s &  18.2s &  1083s  \\  \hline
		MNIST 6$\times$500 & 100\%  & 94\%  & 41\%  & 43\%  & 44\%   \\ 
		$\epsilon = 0.035$ & &  & 6.4s &  16.4s &  1003s  \\  \hline
		CIFAR CNN-B-adv & 78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
		$\epsilon = 2/255$&  &  & 4.3s & 8.7s & 373s  \\ \hline \hline
		CIFAR ResNet & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
		$\epsilon = 2/255$ &  &  & 2s & 2s & 2s  \\ \hline
	\end{tabular}
	\caption{Images verified by $\alpha,\beta$-Crown with different time-outs (TO) on 7 DNNs, and average runtime per image. The 6 first DNNs are hard instances. The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.}
	\label{table_beta}
	\vspace{-0.3cm}
\end{table}

\begin{table}[b!]
	\centering
	\begin{tabular}{||l|c|c||c|c|c||}
		\hline
		Network &  Accuracy & Upper  & Marabou 2.0 & NNenum? &  Full MILP  \\ \hline
		MNIST 5$\times$100 & 99\% & 90\% & 28\% & $\approx 46\%$ & 40 \%    \\
		$\epsilon = 0.026$ & &  &6200s &  5220s & 6100s
		  \\  \hline
		  MNIST 5$\times$100 & 99\% & 90\% & 28\% & $40\%$ & 37 \%    \\
		  TO=2000s & &  & 1250s  & 1343s & 1466s \\  \hline	
	\end{tabular}
\caption{Complete verifiers run on the smallest of the hard DNN with TO = 10 000s. 
%Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and 
No complete verifier could outperform $\alpha,\beta$-CROWN (40\%, 1026s), despite the much larger runtime.}
\label{table_complete}
\end{table}
